\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/applications.tex
first pass with rebuttals
add comment and change proposals

@@

%% I feel like we should mention a bit about the interaction complexity. But that's a bit out of the scope of this paper.
%% Participants rated the ease of control of particular appliances differently. Ease of use ratings were higher for the lamp and fan which had simple, discrete on/off actions, and lower for the more complex movie player (see Figure~\ref{fig:smarthome-likert}). Multiple participants remarked that the difficulty was based on the affordances of Glass: \studyquote{Most of the difficulty I had with Glass came from having to navigate the interface on the tiny screen with the touch pad}. The screen size and (largely) 1D input put a limit on the complexity of interfaces that can be presented. As one participant remarked: \studyquote{[The media player] does not seem to be more efficient than a tablet device.} The difficulty can also partly be ascribed to our interaction design, which required one finger swipes to switch between parameters and two finger gestures for adjusting parameters --- it was hard for users to exert fine control over two-finger swipes. In addition, users did not always remember these mappings as they are not yet part of a standard gesture vocabulary.

>>>>

\ben{We may need to add some discussion of applications}.

@@

\sean{here are some parts I can think of to add to this section, feel free to refine/elaborate/remove.}

\changes{During our study, we learned a few things. (1)Our soulution works best on simple applications such as on/off or volume up/down controls. For more complicated controls, we suggest to use a hybrid solution in which HOBS completes the target selection process and seamlessly transfer information to user's smartphone and triggers corresponding app.  (2)Our solution excels at tasks where the user needs to focus primarily on the objects and the information provided by the near-eye display is only supportive, for example, museums or automobile body shops. (3)Our soulution also works well for roles whose hands are constantly occupied from using handheld devices, e.g. chefs.}
%% I feel like we should mention a bit about the interaction complexity. But that's a bit out of the scope of this paper.
%% Participants rated the ease of control of particular appliances differently. Ease of use ratings were higher for the lamp and fan which had simple, discrete on/off actions, and lower for the more complex movie player (see Figure~\ref{fig:smarthome-likert}). Multiple participants remarked that the difficulty was based on the affordances of Glass: \studyquote{Most of the difficulty I had with Glass came from having to navigate the interface on the tiny screen with the touch pad}. The screen size and (largely) 1D input put a limit on the complexity of interfaces that can be presented. As one participant remarked: \studyquote{[The media player] does not seem to be more efficient than a tablet device.} The difficulty can also partly be ascribed to our interaction design, which required one finger swipes to switch between parameters and two finger gestures for adjusting parameters --- it was hard for users to exert fine control over two-finger swipes. In addition, users did not always remember these mappings as they are not yet part of a standard gesture vocabulary.

### 2014-06-27 doc/sui14/intro.tex
add comment and change proposals

>>>>

\sean{Ben mentioned about discussing the limitations of list approach. Below is the paragraph from chi submission for your reference.}

\changes{ Today, commercial solutions (such as Belkin WeMo) use handheld mobile devices as {\em universal remote controls} to control such appliances. In these solutions, users first browse a list of all available devices and then call up a device-specific user interface. This method faces two challenges: {\em naming} and {\em scoping}. Assigning clear names is non-trivial. In shared spaces, the person trying to control the device might not be the one that named it - e.g., while an office building manager may know what ``Light 4 in area E'' corresponds to, an occupant may not. Second, without a method of scoping selection to automatically filter non-relevant devices, paging though long lists of names or navigating hierarchies becomes potentially more cumbersome than the physical action the ``convenient'' software solution was meant to replace.}
